this is a firt version of the game

now in the game we have..
 v.0.0.1 (pre-beta-test)

  - Main Menu — Always shows on startup; "Load World" button is disabled until at least one save exists
  - World Management — Create, load, delete, import, export worlds. Saves are stored as real JSON files on disk
  (persistent across sessions)
  - Factory System — Create, delete, switch between, and rename multiple factories
  - Building Placement — Place, delete, rotate (R key), toggle on/off (E key) 15 building types on a grid
  - Building Categories (3 tabs) — Extraction, Processing, Manufacturing
  - Connection System — Shift+Click source building, then Shift+Click target to link them. Resources flow through
   connections
  - Production Pipeline — Resources flow: producer → conveyor → consumer/storage, with real-time progress bars
  - Resource Types (9) — Biomass, Blood Algae, Carbon, Enzyme, Polymer, Biofuel, Protein, Bio Component, Bio
  Organ
  - Energy System — Toggleable. Furnaces generate energy, machines consume it. Warning shown when below 30%
  - Development Stages (6) — First Cell → Embryo → Neural Tube → Heartbeat → Organogenesis → Birth. Requires
  production cycles + time + stored resources to advance
  - Stage Unlock System — Buildings unlock progressively per stage. Shows cinematic + modal listing newly
  unlocked machines
  - Cinematic System — Narrated story scenes per stage with auto-advance and skip button
  - Tutorial — 5-page guided tutorial with angel portrait, covers basics, connections, energy, and production
  chain
  - Particle System — Smoke from furnaces, sparks from machines, celebration particles on stage advance
  - Audio System — Procedural sound effects (place, delete, connect, produce, advance, tutorial chime).
  Background ambient drone hum
  - Camera Controls — WASD to pan, scroll to zoom. Speed configurable in settings
  - Right Toolbar — Build / Delete / Inspect tool modes (hotkeys 1 / 2 / 3)
  - Collapsible UI Panels — Sidebar, right resource bar, and right toolbar can each be toggled collapsed
  - Resource Display — Dual display: bottom bar (supply vs demand) and sidebar (per-building totals)
  - Production Stats — Active building count, total production history per resource type
  - Storage System (Blood Sac) — Stores up to 100 units. Can filter which resources to push to output. Receives
  from inputs, pushes to outputs
  - Smart Conveyor — Filterable resource transport. Select which resource types are allowed through
  - Settings Panel — Camera speed, zoom speed, grid size, grid toggle, particles toggle, energy system toggle,
  sound volume, key binding remapper
  - Save System — Auto-save every 30 seconds. File-based JSON saves in Electron (persistent on disk).
  localStorage fallback for browser mode
  - Version Label — Reads VERSION file, displays v.0.0.1 (pre-beta-test) faded in bottom-right corner
  - Quit to Desktop — Saves game then closes the window from the main menu
